Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-05-18 2016_ICML/cmrs.tex
Adressing R3

Bayesian optimization \citep[BO,][]{shahriari_taking_2016} denotes a sequential,
model-based, global approach for optimizing black-box functions that are
non-convex, do not necessarily provide derivatives, are expensive to evaluate (either
computationally, economically, or morally), and are potentially noisy. Under
these conditions, there is typically no guarantee for finding the true optimum of the
function with a finite number of function evaluations. Instead, one often aims
at finding a solution which has small \emph{immediate regret} with regard to the true optimum, where 
``immediate regret'' denotes the difference of the true optimal function value 
and the function value of the selected solution. BO
aims at finding such a solution of minimum immediate regret while  minimizing at the same
time the number of evaluations of the expensive target function. For this, BO
maintains a probabilistic surrogate model of the objective function, and a
myopic utility or acquisition function, which defines the ``usefulness'' of
performing an additional function evaluation at a certain input for learning about the optimum.

BO has been applied to a diverse set of problems, ranging from automatic  machine
learning \cite{bergstra_algorithms_2011,snoek_practical_2012} over robotics
\cite{calandra_bayesian_2015,lizotte_automatic_2007,kroemer_combining_2010,alonso_an_2015} to
sensor networks \cite{srinivas_gaussian_2010} and environmental monitoring
\cite{6385653}. For a more comprehensive overview of application areas, we refer
to \citet{shahriari_taking_2016}.

>>>>

Bayesian optimization \citep[BO,][]{shahriari_taking_2016} denotes a sequential,
model-based, global approach for optimizing black-box functions. It is particularly well-suited for problems
which are non-convex, do not necessarily provide derivatives, are expensive to evaluate (either
computationally, economically, or morally), and can potentially be noisy. Under
these conditions, there is typically no guarantee for finding the true optimum of the
function with a finite number of function evaluations. Instead, one often aims
at finding a solution which has small \emph{immediate regret} with regard to the true optimum, where 
``immediate regret'' denotes the difference of the true optimal function value 
and the function value of the ``solution'' selected by the algorithm after a finite number of function evaluations. BO
aims at finding such a solution of small immediate regret while  minimizing at the same
time the number of evaluations of the expensive target function. For this, BO
maintains a probabilistic surrogate model of the objective function, and a
myopic utility or acquisition function, which defines the ``usefulness'' of
performing an additional function evaluation at a certain input for learning about the optimum.

BO has been applied to a diverse set of problems, ranging from hyperparameter optimization
of machine learning models \cite{bergstra_algorithms_2011,snoek_practical_2012} over robotics
\cite{calandra_bayesian_2015,lizotte_automatic_2007,kroemer_combining_2010,alonso_an_2015} to
sensor networks \cite{srinivas_gaussian_2010} and environmental monitoring
\cite{6385653}. For a more comprehensive overview of application areas, we refer
to \citet{shahriari_taking_2016}.
